Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-10-07 supplement/index.Rmd
add index

>>>>

# Introduction {-}

This is a rendering of the Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_, and contains two fully worked out examples that could provide a useful template for structuring pre-processing pipelines for your own high-throughput tracking data.

The code and data used here are available on Github at [github.com/pratikunterwegs/atlas-best-practices](https://github.com/pratikunterwegs/atlas-best-practices), and on Zendo at [zenodo/atlas-best-practices](https://doi.org/10.5281/zenodo.4287462).
